---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# canPlotR

<!-- badges: start -->

[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

canPlotR is a browser-based tool to generate and export presentation- and publication-ready plots and figures. canPlotR aims to use an intuitive user interface to wrap `ggplot2` graphing functions to create professional and highly customizable figures required for most use cases.

## Installation

You can install the development version of canPlotR from Github so:

```{r load message=FALSE, warning=FALSE}
# If you don't have the `devtools` package installed, you can install it from CRAN with
# install.packages("devtools")
library(devtools)
install_github("wayneliuq/canplotr")
```

## How to Use

### Preparing the stacked input file

Unlike most common applications for making plots (Excel, GraphPad), canPlotR is designed to use the much more versatile *stacked* tables to make plots.

*To be updated*

### Loading the app

To run canPlotR, load the package and run it:

```{r example, message=FALSE, warning=FALSE}
library(canPlotR)
canPlotR::run_app()
```
